Hybrid recurrent model for regime switching nonstationary time series

### 2021-12-01 iclr2022/hybridmodel_iclr.tex
add ets results and confusion matrix

\begin{table*}
  \caption{Results summary on our 10000ts Fashion dataset. For each metric, we compute the average on all our time series. For our two apporaches using neural network, we trained 10 models with different seeds and we display the mean and the standard deviation of our 10 results.}
  \centering
  \begin{tabular}{lllllll}
    \hline
    &  MASE-mean  & MASE-std & SMAPE-mean & SMAPE-std & OWA-mean & OWA-std  \\
    \hline
     \textit{snaive} & 0.881 & - & 25.27 & - & 1. & -\\
     \textit{thetam}  & 0.844 & - & 24.17 & - & 0.970 & -\\
     \textit{arima} & 0.826 & - & 23.63 & - & 0.949 & -\\
     \textit{stlm} & 0.770 & - & 22.05 & - & 0.882 & -\\
     \textit{tbats} & 0.745 & - & 21.13 & - & 0.850 & -\\
     \textit{lstm-withws} & 0.728 & 0.004 & 20.18 & 0.085 & 0.837 & 0.004\\
     \textit{lstm-nows} & 0.724 & 0.003 & 20.08 & 0.052  & 0.825 & 0.004\\
     \textit{hybrid-withws} & 0.713 & 0.005 & 20.53 & 0.170 & 0.825 & 0.009\\
     \textit{hybrid-nows} & 0.715 & 0.002 & 20.41 & 0.056 & 0.816 & 0.002\\
    \hline
  \end{tabular}
\label{tab:metricresults}
\end{table*}

\begin{table*}
  \caption{Results summary on our 1000ts Fashion dataset.For each metric, we compute the average on all our time series. For our two apporaches using neural network, we trained 10 models with different seeds and we display the mean and the standard deviation of our 10 results.}
  \centering
  \begin{tabular}{lllllll}
    \hline
    &  MASE-mean  & MASE-std & SMAPE-mean & SMAPE-std & OWA-mean & OWA-std  \\
    \hline
     \textit{snaive} & 0.871 & - & 25.29 & - & 1. & -\\
     \textit{thetam}  & 0.849 & - & 24.58 & - & 0.980 & -\\
     \textit{arima} & 0.821 & - & 23.69 & - & 0.951 & -\\
     \textit{stlm} & 0.765 & - & 22.22 & - & 0.885 & -\\
     \textit{lstm-nows} & 0.740 & 0.007 & 20.56 & 0.154 & 0.856 & 0.008\\
     \textit{tbats} & 0.734 & - & 21.19 & - & 0.847 & -\\
     \textit{hybrid-nows} & 0.719 & 0.002 & 20.79 & 0.094 & 0.833 & 0.004\\
    \hline
  \end{tabular}
\label{tab:metricresults}
\end{table*}

@@

>>>>

\begin{table*}
  \caption{Results summary on our 10000ts Fashion dataset. For each metric, we compute the average on all our time series. For our two apporaches using neural network, we trained 10 models with different seeds and we display the mean and the standard deviation of our 10 results.}
  \centering
  \begin{tabular}{lllllll}
    \hline
    &  MASE-mean  & MASE-std & SMAPE-mean & SMAPE-std & OWA-mean & OWA-std  \\
    \hline
     \textit{snaive} & 0.881 & - & 25.27 & - & 1. & -\\
     \textit{thetam}  & 0.844 & - & 24.17 & - & 0.970 & -\\
     \textit{arima} & 0.826 & - & 23.63 & - & 0.949 & -\\
     \textit{ets} & 0.807 & - & 23.58 & - & 0.937 & -\\
     \textit{hybrid-withws-ets} & 0.769 & 0.004 & 22.69 & 0.126 & 0.901 & 0.007\\
     \textit{stlm} & 0.770 & - & 22.05 & - & 0.882 & -\\
     \textit{hybrid-nows-ets} & 0.759 & 0.001 & 22.16 & 0.026 & 0.875 & 0.001\\
     \textit{tbats} & 0.745 & - & 21.13 & - & 0.850 & -\\
     \textit{lstm-withws} & 0.728 & 0.004 & 20.18 & 0.085 & 0.837 & 0.004\\
     \textit{lstm-nows} & 0.724 & 0.003 & 20.08 & 0.052  & 0.825 & 0.004\\
     \textit{hybrid-withws} & 0.713 & 0.005 & 20.53 & 0.170 & 0.825 & 0.009\\
     \textit{hybrid-nows} & 0.715 & 0.002 & 20.41 & 0.056 & 0.816 & 0.002\\
    \hline
  \end{tabular}
\label{tab:metricresults}
\end{table*}

\begin{table*}
  \caption{Results summary on our 1000ts Fashion dataset.For each metric, we compute the average on all our time series. For our two apporaches using neural network, we trained 10 models with different seeds and we display the mean and the standard deviation of our 10 results.}
  \centering
  \begin{tabular}{lllllll}
    \hline
    &  MASE-mean  & MASE-std & SMAPE-mean & SMAPE-std & OWA-mean & OWA-std  \\
    \hline
     \textit{snaive} & 0.871 & - & 25.29 & - & 1. & -\\
     \textit{thetam}  & 0.849 & - & 24.58 & - & 0.980 & -\\
     \textit{arima} & 0.821 & - & 23.69 & - & 0.951 & -\\
     \textit{ets} & 0.801 & - & 24.18 & - & 0.944 & -\\
     \textit{hybrid-nows-ets} & 0.768 & 0.002 & 22.91 & 0.111 & 0.902 & 0.005\\
     \textit{stlm} & 0.765 & - & 22.22 & - & 0.885 & -\\
     \textit{lstm-nows} & 0.740 & 0.007 & 20.56 & 0.154 & 0.856 & 0.008\\
     \textit{tbats} & 0.734 & - & 21.19 & - & 0.847 & -\\
     \textit{hybrid-nows} & 0.719 & 0.002 & 20.79 & 0.094 & 0.833 & 0.004\\
    \hline
  \end{tabular}
\label{tab:metricresults}
\end{table*}

@@

\begin{table*}
  \caption{\textit{tbats} model confusion matrix}
  \centering
  \begin{tabular}{llll}
    \hline
    &  dec-trend-pred  & flat-trend-pred & inc-trend-pred  \\
    \hline
	true-dec-trend & 327 & 1607 & 82 \\
    true-flat-trend & 195 & 5586 & 232 \\
    true-inc-trend & 68 & 1585 & 318 \\
    \hline
  \end{tabular}
  \caption{\textit{hybrid} model confusion matrix}
  \centering
  \begin{tabular}{llll}
    \hline
    &  dec-trend-pred  & flat-trend-pred & inc-trend-pred  \\
    \hline
	true-dec-trend & 250 & 1747 & 19 \\
    true-flat-trend & 131 & 5802 & 80 \\
    true-inc-trend & 33 & 1639 & 299 \\
    \hline
  \end{tabular}
  \caption{\textit{hybrid-withws} model confusion matrix}
  \centering
  \begin{tabular}{llll}
    \hline
    &  dec-trend-pred  & flat-trend-pred & inc-trend-pred  \\
    \hline
	true-dec-trend & 615 & 1365 & 36 \\
    true-flat-trend & 510 & 5374 & 129 \\
    true-inc-trend & 65 & 1444 & 462 \\
    \hline
  \end{tabular}
\label{tab:tbatsclass}
\end{table*}

\begin{table*}
  \caption{\textit{lstm} model confusion matrix}
  \centering
  \begin{tabular}{llll}
    \hline
    &  dec-trend-pred  & flat-trend-pred & inc-trend-pred  \\
    \hline
	true-dec-trend & 447 & 1539 & 30 \\
    true-flat-trend & 444 & 5324 & 245 \\
    true-inc-trend & 66 & 1410 & 495 \\
    \hline
  \end{tabular}
  \caption{\textit{lstm-withws} model confusion matrix}
  %\centering
  \begin{tabular}{llll}
    \hline
    &  dec-trend-pred  & flat-trend-pred & inc-trend-pred  \\
    \hline
	true-dec-trend & 796 & 1161 & 59 \\
    true-flat-trend & 1053 & 4701 & 259 \\
    true-inc-trend & 90 & 1259 & 622 \\
    \hline
  \end{tabular}
\label{tab:lstmclass}
\end{table*}
